FinalManuscript_DISCS_UG

### 2019-04-09 pcsc-paper/parts/00_abstract.tex

This paper presents methods to securely compute transcendental functions such as the natural logarithm and the inverse tangent function within a homomorphic cryptosystem.
First, an extension to the Paillier cryptosystem that allows operations on floating-point numbers is presented. 
Second, protocols using a two-party scheme are described for secure multiplication, division, and exponentiation, in order for such operations to be supported by a partially homomorphic cryptosystem such as the Paillier cryptosystem, where these operations are theoretically infeasible to do under a single-party system.
Finally, new closed-form approximations to the logarithm and the inverse tangent functions are derived using the Gauss--Legendre quadrature, which yield more accurate results than other closed-form approximations that involve a similar number of secure operations.

>>>>

This paper presents methods to securely compute transcendental functions such as the natural logarithm and the inverse tangent function within a homomorphic cryptosystem.
First, an extension to the Paillier cryptosystem that allows operations on floating-point numbers is presented. 
Second, protocols using a two-party scheme are described for secure multiplication, division, and exponentiation, in order for such operations to be supported by a partially homomorphic cryptosystem such as the Paillier cryptosystem, where these operations are theoretically infeasible to do under a single-party system.
Finally, new closed-form approximations to the logarithm and the inverse tangent function are derived using the Gauss--Legendre quadrature, which yield more accurate results than other closed-form approximations that involve a similar number of secure operations.

### 2019-04-09 pcsc-paper/parts/05__00_experiments.tex

\section{Experiments}
We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_arithmetic}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.

>>>>

\section{Experiments on Accuracy}
We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_arithmetic}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.

### 2019-04-09 pcsc-paper/parts/05_testsforaccuracy.tex

\begin{table}[ht]
	\caption{Comparison of logarithm approximation errors under Paillier}
	\label{tab:log_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Original quadrature & Scaled quadrature\\
		\midrule
		$\log 1$ & $0$ & $2.053729 \times 10^{-2}$\\
		$\log 10$ & $2.833179 \times 10^{-2} $ & $2.280124 \times 10^{-1}$\\
		$\log 50$ & $2.170779 \times 10^{-2}$ & $2.437148 \times 10^{-2}$\\
		$\log 100$ & $3.524916 \times 10^{-1}$ & $2.122159 \times 10^{-2}$\\
		$\log 200$ & $8.859869 \times 10^{-1}$ & $1.441611 \times 10^{-1}$\\
		$\log 256$ & $1.098463 \times 10^{0}$ & $1.993136 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=0, xmax=255,
			ymin=1e-3, ymax=1.5,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_log_errs.txt};
		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_log_errs.txt};
		\legend{Scaled quadrature, Original quadrature}
		\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Comparison of logarithm approximation errors under Paillier}
	\label{fig:comp_log}
\end{figure}

@@

\begin{table}[ht]
	\caption{Comparison of inverse tangent approximation errors under Paillier}
	\label{tab:arctan_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Partial sum of Euler's series & Quadrature\\
		\midrule
		$\arctan -1$ & $6.564089 \times 10^{-1}$ & $4.629557 \times 10^{-1}$\\
		$\arctan -0.1$ & $4.523405 \times 10^{-3}$ & $1.451929 \times 10^{-3}$\\
		$\arctan -0.01$ & $4.665260 \times 10^{-6}$ & $1.472027 \times 10^{-6}$\\
		$\arctan 0$ & $0$ & $0$\\
		$\arctan 0.01$ & $4.665228 \times 10^{-6}$ & $1.472020 \times 10^{-6}$\\
		$\arctan 0.1$ & $4.523405 \times 10^{-3} $ & $1.451929 \times 10^{-3}$\\
		$\arctan 1$ & $6.564089 \times 10^{-1} $ & $4.629557 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=-1, xmax=1,
			ymin=1e-7, ymax=1,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_arctan_errs.txt};
		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_arctan_errs.txt};
		\legend{Gauss--Legendre quadrature, Partial sum of Euler's series}
		\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Comparison of inverse tangent approximation errors under Paillier}
	\label{fig:comp_arctan}
\end{figure}

>>>>

\begin{table}[ht]
	\caption{Comparison of logarithm approximation errors under Paillier for selected inputs}
	\label{tab:log_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Original quadrature & Scaled quadrature\\
		\midrule
		$\log 1$ & $0$ & $2.053729 \times 10^{-2}$\\
		$\log 10$ & $2.833179 \times 10^{-2} $ & $2.280124 \times 10^{-1}$\\
		$\log 50$ & $2.170779 \times 10^{-2}$ & $2.437148 \times 10^{-2}$\\
		$\log 100$ & $3.524916 \times 10^{-1}$ & $2.122159 \times 10^{-2}$\\
		$\log 200$ & $8.859869 \times 10^{-1}$ & $1.441611 \times 10^{-1}$\\
		$\log 256$ & $1.098463 \times 10^{0}$ & $1.993136 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=0, xmax=255,
			ymin=1e-3, ymax=1.5,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_log_errs.txt};
		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_log_errs.txt};
		\legend{Original quadrature, Scaled quadrature}
		\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Comparison of logarithm approximation errors under Paillier over the interval $[0, 255]$}
	\label{fig:comp_log}
\end{figure}

@@

\begin{table}[ht]
	\caption{Comparison of inverse tangent approximation errors under Paillier for selected inputs}
	\label{tab:arctan_approximation}
	\begin{tabular}{lcc}
		\toprule
		Input & Partial sum of Euler's series & Quadrature\\
		\midrule
		$\arctan -1$ & $6.564089 \times 10^{-1}$ & $4.629557 \times 10^{-1}$\\
		$\arctan -0.1$ & $4.523405 \times 10^{-3}$ & $1.451929 \times 10^{-3}$\\
		$\arctan -0.01$ & $4.665260 \times 10^{-6}$ & $1.472027 \times 10^{-6}$\\
		$\arctan 0$ & $0$ & $0$\\
		$\arctan 0.01$ & $4.665228 \times 10^{-6}$ & $1.472020 \times 10^{-6}$\\
		$\arctan 0.1$ & $4.523405 \times 10^{-3} $ & $1.451929 \times 10^{-3}$\\
		$\arctan 1$ & $6.564089 \times 10^{-1} $ & $4.629557 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogyaxis}[
			xmin=-1, xmax=1,
			ymin=1e-7, ymax=1,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_arctan_errs.txt};
		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_arctan_errs.txt};
		\legend{Partial sum of Euler's series, Gauss--Legendre quadrature}
		\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Comparison of inverse tangent approximation errors under Paillier over the interval $[-1, 1]$}
	\label{fig:comp_arctan}
\end{figure}

% \subsection{Timing Results}
% Timing data was based on a laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM.

% \begin{figure}[!ht]
% 	\centering
% 	\begin{tikzpicture}
% 		\begin{axis}[
% 			% xmin=0, xmax=255,
% 			ytick={1,2},
% 			yticklabels={Scaled quadrature, Original quadrature},
% 			xlabel={Time (seconds)},
% 			grid=major,
% 			legend pos=north east,
% 			legend cell align=left,
% 		]
% 		\addplot+[boxplot, thick, ACMDarkBlue] table[x=x, y=newt] {plots/comp_log_errs.txt};
% 		\addplot+[boxplot, thick, ACMOrange] table[x=x, y=oldt] {plots/comp_log_errs.txt};
% 		\end{axis}
% 	\end{tikzpicture}%
% 	\caption{Comparison of logarithm computation times under Paillier}
% 	\label{fig:times_log}
% \end{figure}

% \begin{figure}[!ht]
% 	\centering
% 	\begin{tikzpicture}
% 		\begin{axis}[
% 			% xmin=0, xmax=255,
% 			ytick={1,2},
% 			yticklabels={Gauss--Legendre quadrature, Euler's series},
% 			xlabel={Time (seconds)},
% 			grid=major,
% 			legend pos=north east,
% 			legend cell align=left,
% 		]
% 		\addplot+[boxplot, thick, ACMDarkBlue] table[x=x, y=newt] {plots/comp_arctan_errs2.txt};
% 		\addplot+[boxplot, thick, ACMOrange] table[x=x, y=oldt] {plots/comp_arctan_errs2.txt};
% 		\end{axis}
% 	\end{tikzpicture}%
% 	\caption{Frequency distribution of inverse tangent computation times under Paillier}
% 	\label{fig:times_arctan}
% \end{figure}

% \begin{figure}[!ht]
% 	\centering
% 	\begin{tikzpicture}
% 		\begin{axis}[
% 			xmin=0, xmax=1,
% 			ymin=1.5, ymax=2.5,
% 			xlabel={Absolute error}, ylabel={Time (seconds)},
% 			grid=major,
% 			legend pos=south east,
% 			legend cell align=left,
% 			tick scale binop=\times,
% 		]
% 		\addplot+[scatter, only marks, ACMDarkBlue] table[x=newerr, y=newt] {plots/comp_arctan_errs2.txt};
% 		\addplot+[scatter, only marks, ACMOrange] table[x=olderr, y=oldt] {plots/comp_arctan_errs2.txt};
% 		\legend{Gauss--Legendre quadrature, Partial sum of Euler's series}
% 		\end{axis}
% 	\end{tikzpicture}%
% 	\caption{Accuracy vs. time in inverse tangent computation under Paillier}
% 	\label{fig:acc_vs_time_arctan}
% \end{figure}

### 2019-04-09 pcsc-paper/parts/06_conclusionreccomendations.tex

\section{Recommendations}
Further research can be done regarding implementation of other transcendental functions, either by using known infinite series, or by using identities with the quadrature-based approximations we have presented in this paper. Different methods for numerical integration can also be explored and applied for use in deriving formulas for privacy-preserving computation. Furthermore, testing with other types of homomorphic cryptosystems can be done, to potentially reduce noise encountered in secure floating-point operations.

>>>>

\section{Recommendations}
Further research can be done regarding implementation of other transcendental functions, either by using known infinite series, or by using identities with the quadrature-based approximations we have presented in this paper. Different methods for numerical integration can also be explored and applied for use in deriving formulas for privacy-preserving computation. Furthermore, testing with other types of homomorphic cryptosystems can be done to potentially reduce noise encountered in secure floating-point operations. Additional testing to determine time efficiency among approximation methods under various homomorphic cryptosystems can also be done.
